%-------------------------
% Complete Resume - Daniel Alfredo Barreras Meraz
% Contains ALL experience, projects, certifications
% Use this as the master source; create tailored versions by commenting out sections
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Daniel Alfredo Barreras Meraz} \\ \vspace{1pt}
    \small 617-685-9017 $|$ \href{mailto:danielbarreras.ab@hotmail.com}{\underline{danielbarreras.ab@hotmail.com}} $|$
    \href{https://linkedin.com/in/danielbrmz}{\underline{linkedin.com/in/danielbrmz}} $|$
    \href{https://github.com/DanielBrMz}{\underline{github.com/DanielBrMz}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tecnol\'ogico de Monterrey (ITESM)}{Guadalajara, MX}
      {B.S. in Computer Science and Technology, GPA: 98/100}{Expected Graduation: Dec. 2026}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    % ===== CAPITAL ONE =====
    \resumeSubheading
      {Lead Software Engineer, Full Stack}{Jun. 2026 -- [Incoming]}
      {Capital One, Enterprise Platforms Technology}{Mexico City, MX}
      \resumeItemListStart
        \resumeItem{Lead a team of engineers building distributed microservices and full-stack systems across Capital One's enterprise platforms, delivering cloud-native AWS solutions serving millions of customers.}
        \resumeItem{Drive technical direction and mentor engineers, collaborating with product managers to translate regulatory and customer needs into scalable architecture.}
        \resumeItem{Design distributed event-driven systems using Java, Kafka, and Kinesis for high-throughput financial data processing at enterprise scale.}
        \resumeItem{Spearhead adoption of container orchestration (Docker, Kubernetes) and open-source frameworks to modernize deployment workflows and accelerate delivery cycles.}
      \resumeItemListEnd

    % ===== BCH / HMS =====
    \resumeSubheading
      {Research Engineer}{Jul. 2025 -- Present}
      {Harvard Medical School -- Boston Children's Hospital (FNNDSC)}{Boston, MA}
      \resumeItemListStart
        \resumeItem{Designed and trained FetEnhNet, a tissue-conditioned deep learning architecture for fetal MRI enhancement, achieving +4.48 dB PSNR across 10,000+ volumetric samples from 6 global sites.}
        \resumeItem{Built production-scale ETL pipeline reducing batch processing time 75\% via parallel processing and Docker containerization, under strict HIPAA/IRB compliance.}
        \resumeItem{Developed ActivSparse-SLM, a 125M sparse LLM combining SLTrain, DeepSeekMoE, and Wanda pruning — 50\% FFN weight sparsity with only +0.3\% perplexity degradation.}
        \resumeItem{Adapted IGUANe CycleGAN from adult T1 to fetal T2-weighted MRI for cross-site scanner harmonization across 6 global acquisition protocols.}
      \resumeItemListEnd

    % ===== SIDEPOCKET =====
    \resumeSubheading
      {Sr Full Stack Engineer}{Nov. 2023 -- Dec. 2025}
      {Sidepocket Inc}{San Francisco, CA (Remote)}
      \resumeItemListStart
        \resumeItem{Scaled fintech microservices from 2K to 15K users handling 2M+ daily transactions at sub-200ms latency, maintaining 99.9\% uptime and cutting infrastructure costs 30\%.}
        \resumeItem{Eliminated 85\% CI/CD manual overhead via infrastructure-as-code on AWS ECS; mentored 3 engineers through rapid team growth.}
        \resumeItem{Architected Redis-to-S3 Parquet migration across 8 microservices, replacing ElastiCache for cost reduction and improved query flexibility.}
        \resumeItem{Designed server-side filtered cache endpoints reducing wire transfer from 60MB to matching rows only, improving high-frequency portfolio query performance.}
      \resumeItemListEnd

    % ===== CIENA =====
    \resumeSubheading
      {Database Administrator}{Jun. 2024 -- Aug. 2025}
      {Ciena Corp}{Zapopan, MX}
      \resumeItemListStart
        \resumeItem{Developed Python-based workflow automation with AWS CloudWatch integration, eliminating 70\% manual operations while processing 10M+ daily records across Oracle EBS infrastructure.}
        \resumeItem{Accelerated mission-critical PL/SQL queries 45\% (2.1s to 800ms) by applying indexing strategies, execution plan analysis, and query refactoring across distributed databases.}
        \resumeItem{Designed real-time database health monitoring and alerting pipelines via AWS CloudWatch, enabling proactive detection of performance regressions across critical Oracle EBS modules.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd

%-----------RESEARCH & ML PROJECTS-----------
\section{Research \& ML Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\href{https://github.com/jbric16/FlameForecast_Project}{\textbf{Phoenix Eye: AI Wildfire Detection}} $|$ \emph{Python, TensorFlow, Next.js, Mapbox, Azure}}{Sep. 2023 -- Dec. 2024}
      \resumeItemListStart
        \resumeItem{Trained a multi-class CNN on 50,000+ MODIS/Landsat satellite images achieving 95\% wildfire detection accuracy; integrated real-time geospatial inference with Mapbox GL 3D terrain rendering and time-control playback on a Next.js frontend.}
        \resumeItem{Deployed end-to-end on Azure with real-time alert pipelines; recognized as NASA Space Apps Global Finalist (Top 40 / 5,000+ teams) and Dubai Prototypes for Humanity 2024 Finalist.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, JavaScript/TypeScript, C++, Go, Rust, PL/SQL, MATLAB, R, Scala} \\
     \textbf{ML \& AI}{: PyTorch, TensorFlow, Computer Vision, Deep Learning, Geospatial Analysis, NLP, scikit-learn, nibabel} \\
     \textbf{Backend}{: Spring Boot, Flask, FastAPI, Microservices, Distributed Systems, RESTful APIs, GraphQL, ZeroRPC} \\
     \textbf{Cloud \& DevOps}{: AWS (ECS, Lambda, RDS, S3, CloudWatch, EC2), Docker, Kubernetes, CI/CD, Terraform, OCI} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, Oracle (EBS, PL/SQL), DynamoDB, Redis, Workflow Automation, ETL Pipelines} \\
     \textbf{Frontend}{: React, Next.js, Vue.js, D3.js, Mapbox, Geospatial Visualization, HTML5/CSS3}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
