%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Daniel Alfredo Barreras Meraz} \\ \vspace{1pt}
    \small +52 642-114-6724 $|$ \href{mailto:danielbarreras.ab@hotmail.com}{\underline{danielbarreras.ab@hotmail.com}} $|$ 
    \href{https://linkedin.com/in/danielbrmz}{\underline{linkedin.com/in/danielbrmz}} $|$
    \href{https://github.com/DanielBrMz}{\underline{github.com/DanielBrMz}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Research Engineer}{Aug. 2025 -- Present}
      {Harvard Medical School - Boston Children's Hospital}{Boston, MA}
      \resumeItemListStart
        \resumeItem{Engineered production-scale Python pipeline processing distributed datasets across 6 global medical sites, implementing automated ETL workflows with Docker containerization for 10,000+ volumetric medical samples.}
        \resumeItem{Built scalable data processing infrastructure reducing batch processing time 75\% (3-5 hours to 30-60 minutes) through parallel processing, caching strategies, and workflow optimization across distributed systems.}
        \resumeItem{Orchestrated 8-stage automated workflow for multi-site data acquisition, validation, and processing under strict regulatory compliance (HIPAA, IRB protocols), ensuring data integrity and audit trails for clinical research.}
      \resumeItemListEnd

    \resumeSubheading
      {Sr Full Stack Engineer}{Nov. 2023 -- Present}
      {Sidepocket Inc}{San Francisco, CA (Remote)}
      \resumeItemListStart
        \resumeItem{Spearheaded architecture and mentored 3 engineers while scaling microservices from 2K to 15K users via Flask/Spring Boot design, maintaining 99.9\% uptime and cutting infrastructure costs 30\%.}
        \resumeItem{Delivered high-throughput RESTful APIs handling 2M+ daily transactions with sub-200ms latency via PostgreSQL tuning, Redis caching, and distributed system patterns.}
        \resumeItem{Transformed CI/CD deployment on AWS ECS, eliminating 85\% manual overhead through infrastructure-as-code practices enabling 5x faster releases.}
      \resumeItemListEnd

    \resumeSubheading
      {Database Administrator}{Jun. 2024 -- Aug. 2025}
      {Ciena Corp}{Zapopan, MX}
      \resumeItemListStart
        \resumeItem{Developed Python-based workflow automation with AWS CloudWatch integration, eliminating 70\% manual operations while processing 10M+ daily records across Oracle EBS infrastructure.}
        \resumeItem{Accelerated mission-critical PL/SQL queries 45\% (2.1s to 800ms response) by applying indexing strategies, execution plan analysis, and query refactoring across distributed databases.}
      \resumeItemListEnd

    \resumeSubheading
      {Full Stack Developer}{Feb. 2021 -- Nov. 2023}
      {Molina Group}{Hermosillo, MX}
      \resumeItemListStart
        \resumeItem{Launched Spring Boot microservices supporting 1,200+ geospatially-distributed vineyard locations, generating \$200K+ annual revenue increase through 30\% operational efficiency gains via workflow automation.}
        \resumeItem{Built Next.js frontend with optimized React components and visualization libraries, boosting geospatial rendering performance 50\% and improving user engagement 40\%.}
        \resumeItem{Secured enterprise authentication infrastructure using OAuth2 and AWS Cognito for 600+ users, achieving SOC 2 compliance and establishing role-based access control.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------AI/ML PROJECTS-----------
\section{Research \& ML Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
          {\href{https://github.com/jbric16/FlameForecast_Project}{\textbf{Phoenix Eye: AI Wildfire Detection}} $|$ \emph{Python, TensorFlow, React.js, Azure}}{Sep. 2023 -- Dec. 2024}
          \resumeItemListStart
            \resumeItem{Delivered geospatial ML application achieving 95\% detection accuracy across 50,000+ satellite images. NASA Space Apps Global Finalist (Top 40/5,000+ teams) and Dubai Prototypes for Humanity 2024 Finalist.}
          \resumeItemListEnd
  \resumeSubHeadingListEnd

  %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tecnológico de Monterrey (ITESM)}{Guadalajara, MX}
      {B.S. in Computer Science and Technology, GPA: 98/100}{}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, JavaScript/TypeScript, C++, Go, PL/SQL, MATLAB, R, Scala} \\
     \textbf{ML \& AI}{: PyTorch, TensorFlow, Computer Vision, Deep Learning, Geospatial Analysis, NLP, scikit-learn} \\
     \textbf{Backend}{: Spring Boot, Flask, FastAPI, Microservices, Distributed Systems, RESTful APIs, GraphQL} \\
     \textbf{Cloud \& DevOps}{: AWS (ECS, Lambda, RDS, S3, CloudWatch, EC2), Docker, Kubernetes, CI/CD, Terraform} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, Oracle, DynamoDB, Redis, Workflow Automation, ETL Pipelines} \\
     \textbf{Frontend}{: React, Next.js, Vue.js, D3.js, Geospatial Visualization, HTML5/CSS3}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}